From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-22 paper.tex
Cosine Similarity fixme `fixed`

The cosine similarity is a more reliable measurement between the ground-truth
and the robot measure of the focus of attention as it accounts for temporal
delays.\fixme{this needs to be better justified/explained.}.

>>>>

The Cronbach's $\alpha$ can be defined as an average of the correlations between 
the items or values at the same time step \textit{t}. Therefore, results can vary 
significantly if both sets of values are time shifted. However,
the cosine similarity becomes a useful measurement in this case as it accounts 
for temporal delays. Specifically, the ground-truth values acquired though human 
annotations may not match the measurements of the focuses of attention computed 
by the robot at the exactly same time step \textit{t} even though the correspondent
curves may look very similar in shape.
